---
title: "table make"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Table Making

There are a few packages which can use to make nice tables in RMarkdown
- knitr
- stargazer
- pander
- tables
- ascii

I'll try get through some of them with some examples!

## Using Knitr Package
The kable function in the knitr lets you create basic tables, with a few different formatting options.

```{r}
#install.packages("knitr")
library(knitr)

kable(head(iris), caption="A simple table about flowers")
kable(head(iris), format= 'html', caption="A simple table about flowers")
kable(head(iris), format= 'latex', caption="A simple table about flowers")  #Latex isn't working on my computer
```
##Formatting options
Kableextra has more options

```{r}
#install.packages("kableExtra")

```

```{r}

library(kableExtra)
library(dplyr)

dt <- head(iris)

kable(dt) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

And this is all I get get in a Markdown before we ran out of time! Check out [this link](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html)
